### 2017-10-02 introduction.tex
updates

The verification and validation of ground motion synthetics has received increasing attention in recent years due to advances in deterministic and non-deterministic physics-based earthquake ground motion simulation. Various methods or schemes have been proposed to evaluate, quantitatively, the misfit or goodness-of-fit (GOF) between simulation synthetics and recorded data or reference alternative solutions \citep{Anderson_2004_Proc, Kristekova_2006_BSSA, Kristekova_2009_GJI, Olsen_2010_SRL, Burks_BSSA_2014, Rezaeian_2015_BSSA}. Among these, there are methods better suited for verification purposes, because they target the comparisons at a waveform level \citep{Kristekova_2006_BSSA, Kristekova_2009_GJI}, whereas others evaluate the comparisons through proxies at the structural response level \citep{Burks_BSSA_2014}. The remaining ones, on the other hand, target specific characteristics in the seismograms themselves in both time and frequency, and are thus better suited for high-frequency or broadband simulations, where the expectation of matching seismograms at the waveform level are less relevant, unless dealing with low-frequency (\fmaxleq{1}). From this group, \citep{Anderson_2004_Proc, Olsen_2010_SRL} are preferred because they offer a simple scoring scheme to normalize the GOF scores associated with different metrics on a common scale.

Out of the various validation methods available, \citet{Anderson_2004_Proc} is perhaps the most widely used \citep[e.g.,]{Chaljub_2010_BSSA, Bielak_2010_GJI, Guidotti_2011_SRL, Maufroy_2015_BSSA}. We, in particular, have consistently relied on a modified version of this method for the validation of a series of simulations of the 2008 $M_w$ 5.4 Chino Hills earthquake, and for a larger suite of moderate-magnitude events in southern California \citep{Taborda_2013_BSSA, Taborda_2014_BSSA, Taborda_2016_GJI}. In essence, Anderson's method evaluates the similarity in terms of 10 metrics based on the cumulative strength of the motion (in terms of Arias intensity and absolute energy), the comparative evolution of the signals in time (through normalized Arias and energy integrals), the peak responses (in acceleration, velocity and displacement), the signals' frequency content (in the form of Fourier and response spectra), and their synchronization (through a cross correlation measure). While the strength

@@

Both \citet{Taborda_2013_BSSA} and \citet{Maufroy_2015_BSSA}, for instance, independently suggested the need to add

>>>>

Verification and validation of ground motion synthetics have received increasing attention in recent years due to advances in deterministic and non-deterministic physics-based earthquake ground motion simulation. Various methods or schemes have been proposed to evaluate, quantitatively, the misfit or goodness-of-fit (GOF) between simulation synthetics and recorded data or reference alternative solutions \citep{Anderson_2004_Proc, Kristekova_2006_BSSA, Kristekova_2009_GJI, Olsen_2010_SRL, Burks_BSSA_2014, Rezaeian_2015_BSSA}. Among these, there are methods better suited for verification purposes, because they target the comparisons at a waveform level \citep{Kristekova_2006_BSSA, Kristekova_2009_GJI}, whereas others evaluate the comparisons through proxies at the structural response level \citep{Burks_BSSA_2014}. The remaining ones, on the other hand, target specific characteristics in the seismograms themselves in both time and frequency, and are thus better suited for high-frequency or broadband simulations, where the expectation of matching seismograms at the waveform level are less relevant, unless dealing with low-frequency (\fmaxleq{1}). From this group, \citep{Anderson_2004_Proc, Olsen_2010_SRL} are preferred because they offer a simple scoring scheme to normalize the GOF scores associated with different metrics on a common scale.

Out of the various validation methods available, \citet{Anderson_2004_Proc} is perhaps the most widely used \citep[e.g.,]{Chaljub_2010_BSSA, Bielak_2010_GJI, Guidotti_2011_SRL, Maufroy_2015_BSSA}. We, in particular, have consistently relied on a modified version of this method for the validation of a series of simulations of the 2008 $M_w$ 5.4 Chino Hills earthquake, and for the evaluation of velocity models in southern California through the validation of a large suite of moderate-magnitude events \citep{Taborda_2013_BSSA, Taborda_2014_BSSA, Taborda_2016_GJI}. In essence, Anderson's method assess the similarity of two signals based on the average scores of 10 metrics. These metrics measure the cumulative strength of ground motion signals (in terms of Arias intensity and absolute energy), the comparative evolution of the signals in time (through normalized Arias and energy integrals), the peak response (in acceleration, velocity and displacement), the signals' frequency content (in the form of Fourier and response spectra), and their synchronization (through cross-correlation).

While the strength of method of \citet{Anderson_2004_Proc} is that its metrics are well understood in engineering and seismology, others have pointed out that some of these metrics are redundant or incomplete. Both \citet{Taborda_2013_BSSA} and \citet{Maufroy_2015_BSSA}, for instance, added a

To remedy

@@

Both , for instance, independently suggested the need to add
